### 2021-07-19 chapters/9_discussion.tex
wip until now

@@

>>>>

We can observe that the distance between the whiskers of the box-plots do not stretch more than the \textit{alpha-value} of 0.05.
This means that there is not one sample that deviated more than 5\% from the original mutation score.
Thus we can reject the null hypothesis and accept our alternative hypothesis.

@@

We can observe that the distance between whiskers of the box-plots is more than the \textit{alpha-value} of 0.05.
Thus we cannot reject the null hypothesis and accept our alternative hypothesis.
